---
title: "Storyboard Template"
output: 
  flexdashboard::flex_dashboard:
    theme: default
    storyboard: true

---

```{r setup, include=FALSE}
library(tidyverse) 
library(inspectdf)
library(tidytuesdayR)
# create www folder
fs::dir_create("www/")
# options for chunks
knitr::opts_chunk$set(
  cache = FALSE,
  echo = TRUE,
  collapse = FALSE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE,
  dev = "ragg_png",
  out.width = '85%',
  fig.path = "www/",
  dpi = 320,
  fig.align = "center",
  fig.width = 7,
  fig.height = 5.5,
  fig.retina = 2
  )
# tibble printing
options(
  pillar.print_max = 10, 
  pillar.print_min = 10)
```


### Background {data-commentary-width=350}

Background information on the dataset...

```{r}




```

*** 

Additional links or sources...

### Data {data-commentary-width=350}

Code for obtaining data...
```{r NFL_Data, eval=FALSE}
library(tidyverse)
library(tidytuesdayR)
NFL_Data <-tidytuesdayR::tt_load("2018-08-28")
nfl_stats <- NFL_Data$`nfl_2010-2017`

```


```{r, echo=FALSE}
nfl_stats <- readr::read_csv("../data/raw/nfl_stats.csv")
```


```{r obtaining_rush_data}
glimpse(nfl_stats)
hi_rsh <- filter(nfl_stats, rush_yds > 200) %>% 
    select(name, rush_yds, starts_with("game"))
hi_rsh %>% 
    count(game_year)

```

```{r obtaining_pas_syds}
glimpse(nfl_stats)
hi_pass <-filter(nfl_stats, pass_yds > 500) %>% 
    select(name, pass_yds, starts_with("game"))
hi_pass %>% 
    count(game_year)
```

```{r obtaining_rec_yds}
glimpse(nfl_stats)
hi_rec <-filter(nfl_stats, rec_yds > 200) %>% 
    select(name, pass_yds, starts_with("game"))
hi_pass %>% 
    count(game_year)

```


```{r obtaining_data}
library(tidyverse)
##install.packages("ggthemes")
library(ggthemes)



```

*** 


Information about the dataset...

### Graphs {data-commentary-width=400}



```{r rushing_yards_graph, echo=FALSE}
labs_grp_bubble <- labs(
    title = "Rushing Attempts Leaders",
    x = "Year", y = "Name", 
    size = "Rushing Yards")

ggp2_grp_bubble <- filter(nfl_stats, rush_att > 33) |> 
    ggplot(aes(
        x = game_year, y = name)) + 
    geom_point(
        aes(size = rush_yds, fill= name), 
        show.legend = FALSE,
        alpha = 2/3, shape = 21, color = "black") +
   scale_size(range = c(1,7), name = "rushing yards")+
    ggthemes::theme_few(base_size = 11)

#color is a fill=rush_yds inside the AES funtcion

ggp2_grp_bubble + 
    labs_grp_bubble

```

***

Code for creating graphs...

```{r, eval=FALSE}
labs_grp_bubble <- labs(
    title = "Rushing Attempts Leaders",
    x = "Year", y = "Name", 
    size = "Rushing Yards")

ggp2_grp_bubble <- filter(nfl_stats, 
                  rush_att > 33) |> 
    ggplot(aes(
        x = game_year, 
        y = name)) + 
    geom_point(
        aes(size = rush_yds,
            fill= name), 
        show.legend = FALSE,
        alpha = 2/3, 
        shape = 21, 
        color = "black") +
   scale_size(range = c(1,7), 
        name = "rushing yards")+
    ggthemes::theme_few(
      base_size = 11)


ggp2_grp_bubble + 
    labs_grp_bubble
```


### Graphs {data-commentary-width=400}

```{r rushing_yds_leaders}
labs_scatter <- labs(
    title = "Highest Rushers",
    x = "game_year", y = "name)")
ggp2_scatter <- filter(nfl_stats, rush_yds > 200)|>
    ggplot(
        aes(x = game_year, 
            y = name)) +
    geom_point()

ggp2_scatter + 
    labs_scatter

```

### Graphs {data-commentary-width=400}

```{r rec_yds_graph_bubble}
labs_grp_bubble <- labs(
    title = "Receptions >15",
    x = "Year", y = "Name", 
    size = "Rushing Yards")

ggp2_grp_bubble <- filter(nfl_stats, rec  > 12) |> 
    ggplot(aes(
        x = game_year, y = name)) + 
    geom_point(
        aes(size = rush_yds, fill= name), 
        show.legend = FALSE,
        alpha = 2/3, shape = 21, color = "black") +
   scale_size(range = c(1,7), name = "rushing yards")+
    ggthemes::theme_few()

#color is a fill=rush_yds inside the AES funtcion

ggp2_grp_bubble + 
    labs_grp_bubble


```

### Graphs {data-commentary-width=400}

```{r rec yds_graph_scatter}
labs_scatter <- labs(
    title = "Highest Recivers",
    x = "game_year", y = "name)")
ggp2_scatter <- filter(nfl_stats, rec_yds > 200)|>
    ggplot(
        aes(x = game_year, 
            y = name)) +
    geom_point()

ggp2_scatter + 
    labs_scatter

```

### Graphs {data-commentary-width=400}

```{r pass_attempts}
labs_grp_bubble <- labs(
    title = "Pass Attempt Leaders",
    x = "Year", y = "Name", 
    size = "Rushing Yards")

ggp2_grp_bubble <- filter(nfl_stats, pass_att  > 55) |> 
    ggplot(aes(
        x = game_year, y = name)) + 
    geom_point(
        aes(size = rush_yds, fill= name), 
        show.legend = FALSE,
        alpha = 2/3, shape = 21, color = "black") +
   scale_size(range = c(1,7), name = "rushing yards")+
    ggthemes::theme_few()

#color is a fill=rush_yds inside the AES funtcion

ggp2_grp_bubble + 
    labs_grp_bubble

```

### Graphs {data-commentary-width=400}

```{r pass_graph}
labs_scatter <- labs(
    title = "Highest Passers",
    x = "game_year", y = "name)")
ggp2_scatter <- filter(nfl_stats, pass_yds > 500)|>
    ggplot(
        aes(x = game_year, 
            y = name)) +
    geom_point()

ggp2_scatter + 
    labs_scatter

```


```{r}
```

*** 

Graphs for data...